The Role of Ice Compositions for Snowlines and the C/N/O Ratios in Active Disks

### 2016-11-03 tex/draft2/ms_revised_2.tex
upd

Figure \ref{fig:CNOstatic}, bottom panel, displays the snowline locations when CO and N$_2$ are in an amorphous porous water environment (see Section \ref{sec:intro}).  The snowlines move outward by a factor of $\sim$3.3 if the ices are pure, and by up to a factor of $\sim$2 for an amorphous compact water substrate (not shown; our estimates are based on the results of \citealt{fayolle16}). The CO snowline moves outward by a factor of $\sim$1.5 if CO is in a crystalline rather than an amorphous porous water environment (not shown; our estimates are based on the results of \citealt{noble12}), and a similar trend is expected for the N$_2$ snowline (see Section \ref{sec:intro}). 
%\textbf{Based on recent observations \citep{luspay16} and theoretical models (\citealt{lectez15}, \citealt{mousis16}) for the composition of comet 67P/Churyumov-Gerasimenko, a fraction of the disk CO (and possibly N$_2$) content may be trapped in clathrates. This would imply CO and N$_2$ snowline locations roughly corresponding to  CO and N$_2$ in a crystalline H$_2$O ice environment as described above.} 
The results of Figure \ref{fig:CNOstatic} thus represent the limiting cases for the positions of the CO and N$_2$ snowlines, for different compositions of the icy grains and morphology of the water ice substrate. This variation in snowline locations changes the chemical abundances both in gas and dust throughout the disk, directly affecting the compositions of nascent giant planets forming in situ. %\textbf{We note that the CO and N$_2$ snowlines will move inward if the ices are in an amorphous compact water environment and slightly shift outward in the case of a crystalline H$_2$O ice substrate.}
\textbf{In our simple model, we ignore the effects of CO and N$_2$ entrapment in water ice through clathrate formation or other processes. Theoretical models aimed at explaining the composition of comet 67P/Churyumov-Gerasimenko suggest that a small fraction of the total CO and N$_2$ reservoir may be trapped in clathrates, and only released upon water sublimation (\citealt{lectez15}, \citealt{mousis16}). In this case, the CO and N$_2$ snowlines would be closer to the star than in the pure ice case.} 
%The importance of this process for CO and N$_2$ is not clear \citep{luspay16}, however, but would in either case not change the locations of the CO and N$_2$ snowlines, i.e. the locations where CO and N$_2$ transition from being mainly present as ice to being mainly present as vapor.}

@@

\acknowledgments{This work is supported by a Simons Collaboration on the Origins of Life (SCOL) investigator award to KIO. JP was supported by the Banneker institute.}

>>>>

Figure \ref{fig:CNOstatic}, bottom panel, displays the snowline locations when CO and N$_2$ are in an amorphous porous water environment (see Section \ref{sec:intro}).  The snowlines move outward by a factor of $\sim$3.3 if the ices are pure, and by up to a factor of $\sim$2 for an amorphous compact water substrate (not shown; our estimates are based on the results of \citealt{fayolle16}). The CO snowline moves outward by a factor of $\sim$1.5 if CO is in a crystalline rather than an amorphous porous water environment (not shown; our estimates are based on the results of \citealt{noble12}), and a similar trend is expected for the N$_2$ snowline (see Section \ref{sec:intro}). 
%\textbf{Based on recent observations \citep{luspay16} and theoretical models (\citealt{lectez15}, \citealt{mousis16}) for the composition of comet 67P/Churyumov-Gerasimenko, a fraction of the disk CO (and possibly N$_2$) content may be trapped in clathrates. This would imply CO and N$_2$ snowline locations roughly corresponding to  CO and N$_2$ in a crystalline H$_2$O ice environment as described above.} 
The results of Figure \ref{fig:CNOstatic} thus represent the limiting cases for the positions of the CO and N$_2$ snowlines, for different compositions of the icy grains and morphology of the water ice substrate. This variation in snowline locations changes the chemical abundances both in gas and dust throughout the disk, directly affecting the compositions of nascent giant planets forming in situ. %\textbf{We note that the CO and N$_2$ snowlines will move inward if the ices are in an amorphous compact water environment and slightly shift outward in the case of a crystalline H$_2$O ice substrate.}
In our simple model, we ignore the effects of CO and N$_2$ entrapment in water ice through clathrate formation or other processes. Theoretical models aimed at explaining the composition of comet 67P/Churyumov-Gerasimenko suggest that a small fraction of the total CO and N$_2$ reservoir may be trapped in clathrates, and only released upon water sublimation (\citealt{lectez15}, \citealt{mousis16}). In this case, the CO and N$_2$ snowlines would be closer to the star than in the pure ice case.
%The importance of this process for CO and N$_2$ is not clear \citep{luspay16}, however, but would in either case not change the locations of the CO and N$_2$ snowlines, i.e. the locations where CO and N$_2$ transition from being mainly present as ice to being mainly present as vapor.}

@@

\acknowledgments{We thank the anonymous referee for helpful comments and suggestions. This work is supported by a Simons Collaboration on the Origins of Life (SCOL) investigator award to KIO. JP was supported by the Banneker institute.}
